---
title: "Grouping and summarizing"
format: html
editor: source
date: "2023-10-11"
output: html_document
---

### Compute basic statistics for all moral dilemma columns. 
Compute the mean, the median, the standard deviation as well as min and max values.
Find meaningful short names for the functions such as `med` for  the median.

Assign `judgments_condition_stats` to the results.

```{r}
# Write your answer here
```



### Sort by groups

Find the number of subjects by `age`, `gender` and `condition`, e.g. how many 20 years of age females are in the `stress` group. 

Sort the resulting tibble such that the condition that contains the most populous group is sorted first (i.e. `stress` or `control` appear together). 

```{r}
# Write your answer here
```

Ensure that the resulting tibble does not contain groups.

### Find the moral dilemma with the highest average score across all participants.

The result must be a tibble containing the dilemma and the average such that the dilemma with the highest average in the first row. 

```{r}
# Write your answer here
```



